The Etiology of Cybersecurity

### 2022-03-07 reports/cimss_2022/main.tex
draft cimsss paper

\documentclass[conference]{IEEEtran}
\usepackage[table]{xcolor}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amsfonts}
\addbibresource{../literature.bib}% Syntax for version >= 1.2
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{amsthm}
\usepackage{rotating}

@@

%fix commands
\newcommand{\fixnote}[2]{\textbf{\color{red}{FIX}}\footnote{{\bf #1:} #2}}
\newcommand{\fix}[2]{{\color{red}{\bf tofix:} #2}}
% \renewcommand{\fixnote}[2]{}
% \renewcommand{\fix}[2]{}

@@

\newtheorem{definition}{Definition}%[section]
\newtheorem{hypothesis}{Hypothesis}%[section]
\newtheorem{theorem}{Theorem}%[section]

@@

\author{
\IEEEauthorblockN{Francesco Beltramini, Federico De Meo, Olivero Nardi, Mattia Pacchin, Marco Rocchetto}
\IEEEauthorblockA{V-Research\\
Verona, Italy\\
Email: knowledgezero@v-research.it}
}

\maketitle

\begin{abstract}
	The objective of this research is to lay the foundations for the
	development of a scientific theory that determines (all and only) the
	possible insecure and secure configurations of any abstract system. We
	claim that cybersecurity weaknesses (i.e. errors) are at the beginning
	of the causality chain that leads to cybersecurity attacks.  We, then,
	formulate a scientific (falsifiable by experiments) hypothesis that we
	use to predict all the weaknesses in the architectural design of an
	abstract system. The mathematical formulation of our hypothesis is
	based on a correlation between the epistemological concepts of
	facts, beliefs, and assertions with the engineering concepts of
	requirements, functional architectures, and channels.  Ultimately, our
	hypothesis allows for the definition of a mathematical formula which
	describes the cybersecurity of a system.  We implemented a prototype
	cybersecurity risk assessment tool that, based on our hypothesis,
	predicts the weaknesses in a UML model of a (cyber-physical) system.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}\label{sec:intro}
\paragraph{Context and motivation} 
A \emph{scientific theory} is an explanation of a phenomenon such that the
explanation follows the scientific method. The \emph{scientific method} is an
\emph{empirical} method that aims at mitigating potential fallacies in
theories.  Karl Popper famously argued (e.g. in \autocite{Popper1959logic})
that a scientific theory can never be verified but only falsified, that a
theory should not be conceived by using the principle of
induction\footnote{Albert  Einstein wrote to Popper: ``[...] and I think (like
you, by the way) that theory cannot be fabricated out of the results of
observation, but that it can only be invented.'' \autocite{Popper1959logic}},
and that empirical experiments should be considered as the only evidence to
support the non-falseness of a scientific theory. 
If we consider a natural (real-world) phenomenon, such as gravity, we can think
of a scientific theory as an \emph{abstract} mathematical formula (or a set of
formulas) that defines axiomatically a certain (natural) phenomenon in a
specific algebraic structure. While such a theory can be proved to be correct
within the mathematical setting it has been conceived in (e.g. with respect to
other axioms of the algebraic structure where it has been postulated, or with
respect to other background theories), no proof can be carried out to verify
that the theory properly abstracts the phenomenon it describes (i.e. that the
theory is a sound or complete approximation of the real phenomenon).
Similarly, the results of the application of a scientific theory (i.e. its
predictions) can be verified in the abstract mathematical structure, but how can
we be sure that the theory correctly characterizes the phenomenon it describes? 
Popper's famous ``demarcation principle'' draws a line between scientific and
pseudo-scientific theories by proposing that a scientific theory can
be considered acceptable as long as no empirical experiment falsify it. For
example, a theory of gravity, in its mathematical setting, can predict how
objects attract each other, and those predictions can be tested by empirical
experiment. If the theory correctly represents the phenomenon, no empirical
experiment should falsify the predictions of that theory.

>>>>

%\documentclass[conference]{llncs}
\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage[table]{xcolor}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amsfonts}
\addbibresource{../literature.bib}% Syntax for version >= 1.2
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{tikz}
%\usepackage{amsthm}
\usepackage{rotating}

@@

%fix commands
\newcommand{\fixnote}[2]{\textbf{\color{red}{FIX}}\footnote{{\bf #1:} #2}}
\newcommand{\fix}[2]{{\color{red}{\bf tofix:} #2}}
\newcommand{\toremove}[2]{{\color{blue}{\bf toremove:} #2}}
% \renewcommand{\fixnote}[2]{}
% \renewcommand{\fix}[2]{}

@@

%\newtheorem{definition}{Definition}%[section]
\newtheorem{hypothesis}{Hypothesis}%[section]
%\newtheorem{theorem}{Theorem}%[section]

@@

\author{Michele Ambrosi\inst{1} \and
Francesco Beltramini\inst{1} \and Federico De Meo\inst{1} \and Olivero Nardi\inst{1} \and Mattia Pacchin\inst{1} \and Marco Rocchetto}

\authorrunning{M. Ambrosi et al.}

\institute{V-Research\\
Verona, Italy\\
\email{knowledgezero@v-research.it}}
\maketitle

\begin{abstract}
	The objective of this research is to lay the foundations for the
	development of a scientific theory that determines (all and only) the
	possible insecure and secure configurations of any abstract system. We
	claim that cybersecurity weaknesses (i.e. errors) are at the beginning
	of the causality chain that leads to cybersecurity attacks.  We, then,
	formulate a scientific (falsifiable by experiments) hypothesis that we
	use to predict all the weaknesses in the architectural design of an
	abstract system. The mathematical formulation of our hypothesis is
	based on a correlation between the epistemological concepts of
	facts, beliefs, and assertions with the engineering concepts of
	requirements, functional architectures, and channels.  Ultimately, our
	hypothesis allows for the definition of a mathematical formula which
	describes the cybersecurity of a system.  We implemented a prototype
	cybersecurity risk assessment tool that, based on our hypothesis,
	predicts the weaknesses in a UML model of a (cyber-physical) system.
  \keywords{Risk Management, Cyber-Physical Systems, Risk Assessment, Security Framework}
\end{abstract}

\section{Introduction}\label{sec:intro}
\fix{mr}{
\begin{enumerate}
  \item Herley's work (1 paragraph)
  \item Implications on Risk Assessment (no theory implies no complete set of weakness which, in turn, implies no risk assessment)
  \item 1 page: contributions
\end{enumerate}
}
\paragraph{Context and motivation} 
A \emph{scientific theory} is an explanation of a phenomenon such that the
explanation follows the scientific method. The \emph{scientific method} is an
\emph{empirical} method that aims at mitigating potential fallacies in
theories.  Karl Popper famously argued (e.g. in \autocite{Popper1959logic})
that a scientific theory can never be verified but only falsified, that a
theory should not be conceived by using the principle of
induction\footnote{Albert  Einstein wrote to Popper: ``[...] and I think (like
you, by the way) that theory cannot be fabricated out of the results of
observation, but that it can only be invented.'' \autocite{Popper1959logic}},
and that empirical experiments should be considered as the only evidence to
support the non-falseness of a scientific theory. 
If we consider a natural (real-world) phenomenon, such as gravity, we can think
of a scientific theory as an \emph{abstract} mathematical formula (or a set of
formulas) that defines axiomatically a certain (natural) phenomenon in a
specific algebraic structure. While such a theory can be proved to be correct
within the mathematical setting it has been conceived in (e.g. with respect to
other axioms of the algebraic structure where it has been postulated, or with
respect to other background theories), no proof can be carried out to verify
that the theory properly abstracts the phenomenon it describes (i.e. that the
theory is a sound or complete approximation of the real phenomenon).
Similarly, the results of the application of a scientific theory (i.e. its
predictions) can be verified in the abstract mathematical structure, but how can
we be sure that the theory correctly characterizes the phenomenon it describes? 
Popper's famous ``demarcation principle'' draws a line between scientific and
pseudo-scientific theories by proposing that a scientific theory can
be considered acceptable as long as no empirical experiment falsify it. For
example, a theory of gravity, in its mathematical setting, can predict how
objects attract each other, and those predictions can be tested by empirical
experiment. If the theory correctly represents the phenomenon, no empirical
experiment should falsify the predictions of that theory.
